Type-Safe Client-Server Communication in Web Applications

### 2014-02-26 paper.tex
Add the beginning of Jen's story to the introduction.

>>>>

To put this all into perspective, let's take a look at the completely fictious
case of Jen, a software developer tasked with implementing a simple ``chatbox''
for a client's web site. Jen is a senior developer, but has no previous
experience with web applications. She is, however, a competend engineer and a
fast learner, and so manages to produce the following piece of client-side code.

\begin{code}
function handshake(sock) {sock.send('helo');}
function chat(sock, msg) {sock.send('text' + msg);}

window.onload = function() {
    var logbox = document.getElementById('log');
    var msgbox = document.getElementById('message');
    var sock = new WebSocket('ws://example.com:24601');

    sock.onmessage = function(e) {
        logbox.value = e.data + NEWLINE + logbox.value;
    };

    sock.onopen = function(e) {
        handshake(sock);
        msgbox.addEventListener('keydown', function(e) {
            if(e.keyCode == 13) {
                var msg = msgbox.value;
                msgbox.value = '';
            }
        });
    };
};
\end{code}

Since the ``chatbox'' application is very simple - users should only be able to
send and receive text messages in real time - Jen opts for a very simple
design. Two UI elements, \lstinline!logbox! and \lstinline!msgbox!, represent
the chat log and the text area where the user inputs their messages
respectively. When a message arrives, it is prepended to the chat log, making
the most recent message appear at the of the log window, and when the user hits
the return key in the input text box the message contained therein is sent and
the input text box is cleared.

Messages are transmitted as strings, with the initial four characters
indicating the type of the message and the rest being the optional payload.
There are only two messages; a handshake indicating that a user wants to join
the conversation, and a broadcast message which sends a line of text to all
connected users via the server.

The code looks solid enough, but Jen is not happy. This simple piece of code
contains no less than three asynchronous callbacks, making the program flow
non-obvious. Moreover, she is concerned about the network communication. The
protocol will clearly need to be redesigned if the application is to be
upgraded with new features later, but the client is not willing to pay Jen to
spend development time on features he has not requested and perhaps never will.
If the protocol will need to be updated in the future, how much time will Jen
need to spend on ensuring that all code using the network protocol stays
updated? Then there is the server component to think; of how much extra work
will it take to ensure that the two code bases stay in sync? Coming from a
desktop background, Jen wonders why something so seemingly simple should
involve client/server architectures and network protocols at all.
